paper

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the file

The table below showcases the general trend on the number of victims in different age group. Age information is based on the year that crime was reported. Adult is considered the group at an age of 18 or older. The age of the youth group is between 12 to 17. Below 12 is considered the child group.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Install the necessary packages if not already installed
install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))

@@

Table 1a counts the total number of victims for each age group over the years. It is obvious to find out that Adult victim group is reported the most and the Child victim group is reported the least. Also, it is noticeable that in 2020, the reported number of victims are far less than the other years. In three different age group, crime reporting rate significantly reduced by the impact of COVID and its lockdown.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create bar graphs for each age group
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
  labs(title = "Number of Reported Victims of Crimes in Different Age Group Over the Years",
       x = "Year",
       y = "Number of reported crimes") +
  scale_fill_manual(values = c(Adult = "blue", Youth = "green", Child = "orange"),
                    name = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

@@

Bar graph 1a refers table 1a. By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult. Also, the bars are showing ascending order from the year 2014 to 2018 but the reported crimes significantly drop between 2019 and 2020. One possible reason is because of COVID. Correlation between COVID pandemic and report crime rates 논문 찾아서 첨부

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create a bar graph for Sexual Violation with groups for AGE_GROUP
bar_plot <- ggplot(sexual_violation_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Victims Count of Sexual Violation by Age Group Over the Years",
       x = "Year",
       y = "Number of Reported Victims of Sexual Violation",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

The graph illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022. COVID does not seem to be a factor that skews the trend. Though, size of both child and youth victim groups got halved. Compared to child victim group, size of youth victim group grows fast.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create a bar graph for Robbery with groups for AGE_GROUP
bar_plot <- ggplot(robbery_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Victims Count of Robbery by Age Group Over the Years",
       x = "Year",
       y = "Number of Reported Victims of Robbery",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(robbery_data$REPORT_YEAR), max(robbery_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))

@@

As of 2018, youth group of victims of robbery diminished and it keeps at the lower level. COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year. In 2020, victims of robbery in every age group significantly decreased. We could assume that lockdown mandate affect the decrease in victims.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create bar graphs for each crime subtype
bar_plot <- ggplot(pivoted_table2, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
  labs(title = "Victims Count by Crime Subtype Over the Years",
       x = "Year",
       y = "Number of Reported Victims of Crimes") +
  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
                    name = "Crime Subtype") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

>>>>

The table (@tbl-totalsum_table) below showcases the general trend on the number of victims in different age group. Age information is based on the year that crime was reported. Adult is considered the group at an age of 18 or older. The age of the youth group is between 12 to 17. Below 12 is considered the child group.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-totalsum-table
#| tbl-cap: "Total sum of victims in different age group throughout the years"

@@

# Install the necessary packages if not already installed
# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))

@@

Table 1a (@tbl-totalsum-table) counts the total number of victims for each age group over the years. It is obvious to find out that Adult victim group is reported the most and the Child victim group is reported the least. Also, it is noticeable that in 2020, the reported number of victims are far less than the other years. In three different age group, crime reporting rate significantly reduced by the impact of COVID and its lockdown.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-totalsum-bar
#| tbl-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"

@@

# Create bar graphs for each age group
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Number of reported crimes") +
  scale_fill_manual(values = c(Adult = "blue", Youth = "green", Child = "orange"),
                    name = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

@@

Bar graph (@tbl-totalsum-bar) refers table (@tbl-totalsum-table). By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult. Also, the bars are showing ascending order from the year 2014 to 2018 but the reported crimes significantly drop between 2019 and 2020. One possible reason is because of COVID. Correlation between COVID pandemic and report crime rates 논문 찾아서 첨부

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-sv-bar
#| tbl-cap: "Victims Count of Sexual Violation by Age Group Over the Years"

@@

# Create a bar graph for Sexual Violation with groups for AGE_GROUP
bar_plot <- ggplot(sexual_violation_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Year",
       y = "Number of Reported Victims of Sexual Violation",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-a-bar
#| tbl-cap: "Victims Count of Assault by Age Group Over the Years"

@@

The graph (@tbl-a-bar) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022. COVID does not seem to be a factor that skews the trend. Though, size of both child and youth victim groups got halved. Compared to child victim group, size of youth victim group grows fast.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-r-bar
#| tbl-cap: "Victims Count of Robbery by Age Group Over the Years"

@@

# Create a bar graph for Robbery with groups for AGE_GROUP
bar_plot <- ggplot(robbery_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Year",
       y = "Number of Reported Victims of Robbery",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(robbery_data$REPORT_YEAR), max(robbery_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))

@@

Graph (@tbl-r-bar) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level. COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year. In 2020, victims of robbery in every age group significantly decreased. We could assume that lockdown mandate affect the decrease in victims.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-crimetype-table
#| tbl-cap: "Total number of victims counted for each crime from the year 2014 to 2022"

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-crimesubtype-bar
#| tbl-cap: "Victims Count by Crime Subtype Over the Years"

@@

# Create bar graphs for each crime subtype
bar_plot <- ggplot(pivoted_table2, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Number of Reported Victims of Crimes") +
  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
                    name = "Crime Subtype") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))
